OptiFit: an improved method for fitting amplicon sequences to existing OTUs

### 2021-12-16 paper/paper_before-review.Rmd
Lock in stats from before the review

---
title: "OptiFit: an improved method for fitting amplicon sequences to existing OTUs"
date: '2021-11-08'
bibliography: references.bib
link-citations: true
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
  github_document:
    html_preview: false
csl: msphere.csl
fontsize: 12pt
geometry: margin=1.0in
params:
  include_figures: false
---

@@

load(here("results", "stats.RData"))

>>>>

---
title: "OptiFit: an improved method for fitting amplicon sequences to existing OTUs"
date: '2021-11-08'
bibliography: references.bib
link-citations: true
output:
  pdf_document:
    includes:
      in_header: preamble.tex
      before_body: head.tex
    fig_caption: yes
    keep_tex: false
  github_document:
    html_preview: false
csl: msphere.csl
fontsize: 12pt
geometry: margin=1.0in
params:
  include_figures: false
---

@@

load(here("results", "stats_before-review.RData"))
